On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~Z.~F. and S.~S.}

### 2018-12-03 tt_theorem.tex
12/3 16pm

\subsubsection{Case of $S[h-1..h+1] = tbt$}
Fig.\ref{TTT_tunnelC_enter_usingTunnel} exhibits all the two kinds of stabilization depending on structures of tunnel C.

\begin{itemize}
\item{Left of Fig.\ref{TTT_tunnelC_enter_usingTunnel}}\\
  In this figure, Bead $n_4$ has at least one binding so that $w[h-1]$ has to bound $n_4$. Moreover, $w[h]$ has to bind to one of $n_1, n_2, n_3$ in order to stabilize deterministically. On the other hand, $w[h+1]$ can supply two bindings but has only two free neighbors. One of them is occupied by a successor. Therefore $w[h+1]$ can only bind one of $n_5, n_6$, that is, $w[h+1]$ supplies at most one binding. Thus, this case $\#bc(C_{h-1}) > \#bc(C_{h+1})$.

\item{Right of Fig.\ref{TTT_tunnelC_enter_usingTunnel}}\\
  These cases are divided on number of capabilities that $w[h-1]$ consumes.
  \begin{itemize}
  \item[-]{$w[h-1]$ does not consume any bindings}\\
  According to Lemma~\ref{TTT_exit}, $\#bc(C_{h-3}) \geq \#bc(C_{h-1})$ because of $S[h-1] = t$.
    $w[h]$ has to bound one of $n_1, n_2, n_3$ in order to stabilize deterministically so that  $\#bc(C_{h-1}) > \#bc(C_{h})$.
    $w[h+1]$ has to be bound to $w[h-1]$ because $w[h-1]$ has bindings, that is, $w[h+1]$ consumes at least one hand and supplies at most one hand so that $\#bc(C_{h}) \geq \#bc(C_{h+1})$. Thus, in this cases $\#bc(C_{h-3}) > \#bc(C_{h+1})$.
%     This time, let us consider either $n_4$ is occupied or not. If $n_4$ is occupied, then $w[h-1]$ has no active bindings that is this situation consumes some binding capabilities. If $n_4$ is free and $w[h+2]$ is stabilized in $n_4$, then $w[h-1]$ has to bind $w[h+2]$. Therefore, In this case, stabilization of $w[h-1..h+2]$ consumes some bindings. If $n_4$ is free and $w[h+2]$ is stabilized except $n_4$, then this oritatami system has to use two binding capabilities in order to bind $w[h+2]$. Therefore, in this case consumes some bindings. Thus in this cases $\#bc(C_{h-1}) > \#bc(C_{h+2})$.

@@

  \end{itemize}
\end{itemize}
\begin{figure}
  \centering
    \begin{tabular}{cc}

@@

\subsection{On structures provided by a unary and $\delta = 1$ oritatami system}
\begin{theorem}[$\delta= 1, \alpha=2$]
Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha = 2$. It can yield infinite structures but they are only zig-zag conformation.
\end{theorem}

@@

\begin{theorem}[$\delta = 1, \alpha = 3$]
Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha = 3$. It can yield only finite structures whose size is $O(n)$.
\end{theorem}

@@

\begin{theorem}[$\delta = 1, \alpha = 4$]
Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha = 4$. It can yield only finite structures whose size is $O(n^2)$.
\end{theorem}

\begin{lemma}
\label{TTT_a4_2b_lemma}
Any beads which are already stabilized by some bonds use at least two bonds.
\end{lemma}

\begin{proof}[proof of lemma]
Let us consider when $w[i]$ is stabilized by only one bond. See Fig.\ref{TTT_a4_lemma_fig}. According to lemma\ref{TTT_neighbor_lemma}, if $n_3$ is free, $w[i-2]$ has some hands. Thus, $n_4$ has to be occupied in order to stabilize deterministically. Moreover, also $n_2$ has to be occupied for deterministic and also $n_0, n_1$. $n_1$ has some hands because $n_3$ is free. Therefore, $w[i]$ is stabilized at $n_3$ and it has to use at least two hands. It contradict assumption.
\end{proof}

\begin{figure}
 \centering
    \begin{tikzpicture}
	\fill[shift=(180:1)] (0,0) circle [radius=0.1];
      \fill[shift=(180:0)] (0,0) circle [radius=0.1];

>>>>

\subsubsection{Case of $S[h-1..h+1] = tbt_a$}
Fig.\ref{TTT_tunnelC_enter_usingTunnel} exhibits all the two kinds of stabilization depending on structures of tunnel C.

%\item{Left of Fig.\ref{TTT_tunnelC_enter_usingTunnel}}\\
  In this figure, Bead $n_4$ has at least one binding so that $w[h-1]$ has to bound $n_4$. Moreover, $w[h]$ has to bind to one of $n_1, n_2, n_3$ in order to stabilize deterministically. On the other hand, $w[h+1]$ can supply two bindings but has only two free neighbors. One of them is occupied by a successor. Therefore $w[h+1]$ can only bind one of $n_5, n_6$, that is, $w[h+1]$ supplies at most one binding. Thus, this case $\#bc(C_{h-1}) > \#bc(C_{h+1})$.

  These cases are divided on number of capabilities that $w[h-1]$ consumes.
  \begin{itemize}
  \item[-]{$w[h-1]$ does not consume any bindings}\\
  According to Lemma~\ref{TTT_exit}, $\#bc(C_{h-3}) \geq \#bc(C_{h-1})$ because of $S[h-1] = t$.
    $w[h]$ has to bound one of $n_1, n_2, n_3$ in order to stabilize deterministically so that  $\#bc(C_{h-1}) > \#bc(C_{h})$.
    $w[h+1]$ has to be bound to $w[h-1]$ because $w[h-1]$ has bindings, that is, $w[h+1]$ consumes at least one hand and supplies at most one hand so that $\#bc(C_{h}) \geq \#bc(C_{h+1})$. Thus, in this cases $\#bc(C_{h-3}) > \#bc(C_{h+1})$.
%     This time, let us consider either $n_4$ is occupied or not. If $n_4$ is occupied, then $w[h-1]$ has no active bindings that is this situation consumes some binding capabilities. If $n_4$ is free and $w[h+2]$ is stabilized in $n_4$, then $w[h-1]$ has to bind $w[h+2]$. Therefore, In this case, stabilization of $w[h-1..h+2]$ consumes some bindings. If $n_4$ is free and $w[h+2]$ is stabilized except $n_4$, then this oritatami system has to use two binding capabilities in order to bind $w[h+2]$. Therefore, in this case consumes some bindings. Thus in this cases $\#bc(C_{h-1}) > \#bc(C_{h+2})$.

@@

\begin{figure}
  \centering
    \begin{tabular}{cc}

@@

\subsection{On structures provided by a unary and $\delta = 1$ oritatami system}

\begin{figure}[tb]
 \centering
    \begin{tikzpicture}
	\fill[shift=(180:1)] (0,0) circle [radius=0.1];
      \fill[shift=(180:0)] (0,0) circle [radius=0.1];

\begin{lemma}
\label{TTT_a4_2b_lemma}
Let $\Xi$ be a deterministic unary oritatami system of $\delta = 1, \alpha = 4$.
When a bead is stabilized by bond, it forms at least two bonds.
\end{lemma}

\begin{proof}%[proof of lemma]
Suppose $w[i]$ were stabilized by only one bond. See Fig.~\ref{TTT_a4_lemma_fig}. If $n_3$ is free, $w[i-2]$ still has some bonds because of arity $\alpha = 4$. Thus, $n_4$ must be occupied; otherwise, $w[i]$ would be stabilized nondeterministically at $n_3$ and $n_4$. Moreover, also $n_2$ has to be occupied for deterministic and also $n_0, n_1$. $n_1$ has some hands because $n_3$ is free. Therefore, $w[i]$ is stabilized at $n_3$ and it has to use at least two hands. It contradict assumption.
\end{proof}

\begin{theorem}[$\delta = 1, \alpha = 4$]
Let $\Xi$ be a deterministic unary oritatami system of $\delta = 1, \alpha = 4$. It can yield only finite conformation of length is $3n^2  + 3n + 1$.
\end{theorem}

\begin{theorem}[$\delta= 1, \alpha=2$]
Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha = 2$. It can yield infinite structures but they are only zig-zag conformation.
\end{theorem}

@@

\begin{theorem}[$\delta = 1, \alpha = 3$]
Let $\Xi$ be a deterministic unary oritatami system of $\delta = 1, \alpha = 3$. It can yield only finite conformations of length is $O(n)$.
\end{theorem}

@@
